\begin{abstract}
\label{sec:abstract}
Software defined network (SDN) is programmable, centrally managed, and flexible with topology alteration. It allows network administrators to manage network flows easily. However, these new features also lead to new security problems with applications, controllers, OpenFlow switches, topology management and so on. In this work, we study the attack of compromising a switch, and design a method to detect disobedient forwarding detection. To enhance the detection efficiency and minimize additional network traffic, we reduce the number of detection packets necessary by aggregating the flow entries in short computation time. To aggregate the flow entries, we select entries whose match fields are able to compose a valid packet from different switches. The switches on which the entries are form a path that allows the packet to travel through, achieving rapid detection.\sout{\red{Add a few sentences to describe how the aggregation is done.}} We evaluate the effectiveness of this method in various topology types in a data center network. The experimental result demonstrates that this method can detect a topology with 20 switches and 400 flow entries in total with around 135 detection packets. In other words, a detection packet can inspect the forwarding correctness of nearly 3 entries simultaneously on average. Furthermore, since the positive and negative factor to the growth of aggregation rates break even, the scale of the network topology does not affect the efficiency of our method significantly \sout{\red{describe why the efficiency is not affected}}.
\end{abstract}