\begin{thebibliography}{1}

\bibitem{NH12}
Adnan Nadeem and Michael P. Howarth,
``A Survey of MANET Intrusion Detection \& Prevention Approaches for Network Layer Attacks,'', In Proc. of IEEE COMMUNICATIONS SURVEYS \& TUTORIALS, VOL. 15, NO. 4, FOURTH QUARTER 2013.

\bibitem{GKPPCMS08}
Natasha Gude, Teemu Koponen, Justin Pettit, Ben Pfaff, Martín Casado, Nick McKeown and Scott Shenker
``NOX: Towards an Operating System for Networks'', ACM SIGCOMM Computer Communication Review 38.3 (2008): 105-110.

\bibitem{EZA11}
EugeneNg, ZhengCai AlanL Cox TS.,
``Maestro: Balancing fairness, latency and throughput in the openflow control plane'', Tech. rep., Rice University, 2011.

\bibitem{KJK}
Anurag Khandelwal, Navendu Jain and Seny Kamara
``Attacking Data Center Networks from the Inside'', 

\bibitem{AAS14}
Markku Antikainen, Tuomas Aura, and Mikko Särelä,
``Spook in Your Network: Attacking an SDN with a Compromised OpenFlow Switch'', In proc. of Springer International Publishing Switzerland 2014.

\bibitem{LNRSW04}
T.V. Lakshman, T. Nandagopal, R. Ramjee, K. Sabnani and T. Woo
``The softrouter architecture'', In Proc. of ACM SIGCOMM Workshop on Hot Topics in Networking. Vol. 2004. 2004.

\bibitem{TTB15}
TIEN THANH BUI,
``Analysis of Topology Poisoning Attacks in Software-Defined Networking'', Degree project in security and mobile computing, Second Level Stockholm, Sweden 2015.

\bibitem{PPTI14}
Farzaneh Pakzad, Marius Portmann, Wee Lum Tan and Jadwiga Indulska,
``Efficient Topology Discovery in Software Defined Networks'', In Signal Processing and Communication Systems (ICSPCS), 2014 8th International Conference on, pp. 1-8. IEEE, 2014. 

\bibitem{CKGL15}
Po-Wen Chi, Chien-Ting Kuo, Jing-Wei Guo and Chin-Laung Lei,
``How to Detect a Compromised SDN Switch'', In Network Softwarization (NetSoft), 2015 1st IEEE Conference on (pp. 1-6). IEEE.

\bibitem{HXWG15}
Sungmin Hong, Lei Xu, Haopei Wang and Guofei Gu,
``Poisoning Network Visibility in Software-Defined Networks: New Attacks and Countermeasures'', In NDSS. 2015. 

\bibitem{ATPP15}
Alharbi, Talal, Marius Portmann, and Farzaneh Pakzad,
``The (In) Security of Topology Discovery in Software Defined Networks.'', In Proc. of Local Computer Networks (LCN), 2015 IEEE 40th Conference on. IEEE, 2015.

\bibitem{KDFRV13}
Kreutz, Diego, Fernando Ramos, and Paulo Verissimo, 
``Towards secure and dependable software-defined networks'', In Proc. of the second ACM SIGCOMM workshop on Hot topics in software defined networking. ACM, 2013.


\bibitem{FFR09}
Ferraiolo, David F., and D. Richard Kuhn., 
``Role-based access controls'', arXiv preprint arXiv:0903.2171 (2009).

\bibitem{}
Hu, Ningning, and Peter Steenkiste,
``Estimating available bandwidth using packet pair probing'', No. CMU-CS-02-166. CARNEGIE-MELLON UNIV PITTSBURGH PA SCHOOL OF COMPUTER SCIENCE, 2002.

\bibitem{HRKC12}
Ralph Holz, Thomas Riedmaier, Nils Kammenhuber, Georg Carle, 
``X. 509 Forensics: Detecting and Localising the SSL/TLS Men-in-the-middle'' , In Computer security–esorics 2012 (pp. 217-234). Springer Berlin Heidelberg.

\bibitem{YZP11}
Yan, Zheng, and Christian Prehofer,
``Autonomic trust management for a component-based software system'', Dependable and Secure Computing, IEEE Transactions on 8.6 (2011)

\bibitem{SPYFGT13}
Shin, S., Porras, P. A., Yegneswaran, V., Fong, M. W., Gu, G., and Tyson, M.,
``FRESCO: Modular Composable Security Services for Software-Defined Networks'', in NDSS 2013.

\bibitem{PSYFTG12}
Phillip Porras, Seungwon Shin, Vinod Yegneswaran, Martin Fong, Mabry Tyson and Guofei Gu,
``A Security Enforcement Kernel for OpenFLow Networks'', In Proc. of the first workshop on Hot topics in software defined networks. ACM, 2012.

\bibitem{OF_SPEC}
\url{https://www.opennetworking.org/images/stories/downloads/sdn-resources/onfspecifications/openflow/openflow-switch-v1.5.1.pdf}

\bibitem{OFDP_GENI}
\url{http://groups.geni.net/geni/wiki/OpenFlowDiscoveryProtocol}

\bibitem{LLDP_WS}
\url{https://wiki.wireshark.org/LinkLayerDiscoveryProtocol}

\bibitem{SSAV_NWW}
\url{http://www.networkworld.com/article/2840273/sdn/sdn-security-attack-vectors-and-sdn-hardening.html}

\bibitem{TTN}
\url{http://www.wipro.com/documents/insights/the-thinking-network.pdf}

\bibitem{HP_SPEC}
\url{http://h10032.www1.hp.com/ctg/Manual/c04495114}

\bibitem{SHELLSHOCK}
\url{https://web.nvd.nist.gov/view/vuln/detail?vulnId=CVE-2014-6271}

\bibitem{POODLE}
\url{https://web.nvd.nist.gov/view/vuln/detail?vulnId=CVE-2014-3566}

\bibitem{HB}
\url{https://web.nvd.nist.gov/view/vuln/detail?vulnId=CVE-2014-0160}

\bibitem{PP}
\url{http://usenix.org/legacy/publications/library/proceedings/usits01/full_papers/lai/lai_html/node2.html}
----------------

\bibitem{ASO08}
T. T. Nguyen and G. Armitage, 
``A Survey Of Techniques for Internet Traffic Classification Using Machine Learning,'' In Proc. of IEEE Comm. Surveys Tutorials, vol. 10, no. 4, pp. 56-76, Oct.-Dec.2008.

\bibitem{PIO13}
J. S. Park, S. H. Yoon and M. S. Kim,
``Performance Improvement of Payload Signature-based Traffic Classification System Using Application Traffic Temporal Locality,'' In Proc. of the 15th Network Operations and Management Symposium (APNOMS), Sept. 2013. 

\bibitem{COS04}
M. Roughan, S. Sen, O. Spatscheck and N. Duffield, 
``Class-of-servicemapping for QoS: a statistical signature-based approach to IP traffic classification,''  In Proc. of ACM SIGCOMM Conference on Internet Measurement, Oct. 2004.

\bibitem{TFT14}
P. C. Lin, S. Y. Chen and C. H. Lin, 
``Towards Fine-grained Traffic Classification for Web Applications,'' In Proc. of Australasian Telecommunication Networks and Applications Conference (ATNAC), Nov. 2014.

\bibitem{TTC}
P. Schneider,
``TCP/IP traffic Classification Based on port numbers,'' Diploma Thesis, Division of Applied Science, Harvard University, 29 Oxford Street, Cambridge, MA 02138, USA, 1-6

\bibitem{TCI13}
Y. Xue, D. Wang and L. Zhang,
``Traffic Classification: Issues and Challenges,'' In Proc. of the International Conference on Computing, Networking and Communications (ICNC), Jan. 2013.

\bibitem{nDPI}
\url{http://www.ntop.org/products/deep-packet-inspection/ndpi/}

\bibitem{l7-filter}
\url{http://l7-filter.clearos.com/}

\bibitem{EMF14}
B. Hullar, S. Laki and A. Gyorgy,
``Efficient Methods for Early Protocol Identification,'' IEEE Journal on Selected Areas in Communications,  vol. 32, issue 10, Oct. 2014. 

\bibitem{EAI06}
L. Bernaille, R. Teixeira and K. Salamatian, 
``Early application identification,'' In Proc. of the Conference on Future Networking Technologies, 2006.

\bibitem{ATC13}
H. M. An, M. S. Kim and J. H. Ham,
``Application traffic classification using statistic signature,'' In Proc. of the 15th Asia-Pacific Network Operations and Management Symposium (APNOMS), Sept. 2013.

\bibitem{AIS14}
B. Schmidt, D. Kountanis and A. Al-Fuqaha, 
``Artificial Immune System Inspired Algorithm for Flow-Based Internet Traffic Classification,'' In Proc. of the IEEE 6th International Conference on Cloud Computing Technology and Science (CloudCom), Dec. 2014. 

\bibitem{FPN13}
S. Tapaswi and A. S. Gupta,
``Flow-Based P2P Network Traffic Classification Using Machine Learning,'' In Proc. of the International Conference on Cyber-Enabled Distributed Computing and Knowledge Discovery (CyberC), Oct. 2013. 

\bibitem{RTC10}
F .Dehghani, N .Movahhedinia, M. R. Khayyambashi and S. Kianian, 
``Real-Time Traffic Classification Based on Statistical and Payload Content Features,'' In Proc. of the 2nd International Workshop on Intelligent Systems and Applications (ISA), May 2010. 

\bibitem{ASA09}
S. Huang, K. Chen, C. Liu, A. Liang and H. Guan,
``A statistical-feature-based approach to internet traffic classification using Machine Learning,'' In Proc. of the International Conference on Ultra Modern Telecommunications and Workshops (ICUMT), Oct. 2009. 

\bibitem{FTC09}
M. Kohara, T. Hori, K. Sakurai, H. Lee and J. C. Ryou,
``Flow Traffic Classification with Support Vector Machine by Using Payload Length,'' In Proc. of the 2nd International Conference on Computer Science and its Applications (CSA), Dec. 2009.  

\bibitem{CMF04}
M. Roughan, S. Sen, O. Spatscheck and N. Duffield, 
``Class-of-Service Mapping for Qos: A Statistical Signature-based Approach to IP Traffic Classification,'' In Proc. of the Internet Measurement Conference (IMC), Oct. 2004.

\bibitem{COC12}
J. Zhang, C. Chen, Y. Xiang and W. Zhou, 
``Classification of Correlated Internet Traffic Flows,'' In Proc. of the 11th IEEE International Conference on Trust, Security and Privacy in Computing and Communications (TrustCom), June 2012.

\bibitem{FBC11}
S. Valenti and D. Rossi, 
``Fine-grained behavioral classification in the core: the issue of flow sampling,'' In Proc. of the 7th International Wireless Communications and Mobile Computing Conference (IWCMC), July 2011.
 
\bibitem{TFT11}
B. Park, J. W. Hong and Y. J. Won,
``Toward Fine-Grained Traffic Classification,'' IEEE Communication Magazine, vol. 49, issue. 7, pp. 104-111, July 2011. 
 
\bibitem{OTP11}
B. Augustin and A. Mellouk,
``On Traffic Patterns of HTTP Applications,'' In Proc. of the IEEE Global Communications Conference (GLOBECOM), Dec. 2011. 
 
\bibitem{DHC11}
R. Archibald, Y. Liu, C. Corbett and D. Ghosal, 
``Disambiguating HTTP: Classifying web Applications,'' In Proc. of the 7th International Wireless Communications and Mobile Computing Conference (IWCMC), July 2011.

\bibitem{MAM13}
P. Casas and P. Fiadino, 
``Mini-IPC: A minimalist approach for HTTP traffic classification using IP addresses,'' In Proc. of the 9th International Wireless Communications and Mobile Computing Conference (IWCMC), July 2013.
 
\bibitem{libnids}
\url{http://libnids.sourceforge.net}.  

\bibitem{AAM10}
M. Lee, R. R. Kompella and S. Singh, 
``Ajaxtracker: active measurement system for high-fidelity characterization of Ajax applications,'' In Proc. of the 2010 USENIX conference on Web application development (WebApps '10), 2010.  

\bibitem{MTC09}
S. Veres and D. Ionescu, 
``Measurement-based traffic characterization for Web 2.0 applications,'' In Proc. of the IEEE Instrumentation and Measurement Technology Conference (I2MTC), May 2009.
 
\bibitem{COH08}
L. Shuai, G. Xie and J. Yang,
``Characterization of HTTP behavior on access networks in Web 2.0,'' In Proc. of the International Conference on Telecommunications (ICT), June 2008.

\bibitem{WTM09}
S. Lin, Z. Gao and K. Xu, 
``Web 2.0 traffic measurement: analysis on online map applications,'' In Proc. of the 18th International Workshop on Network and Operating Systems Support for digital audio and video, ser. NOSSDAV ’09, 2009.

\bibitem{HTTP2}
M. Belshe, BitGo, R. Peon and M. Thomson, Ed., ``Hypertext Transfer Protocol Version 2 (HTTP/2),'' RFC 7540, May 2015.

\bibitem{IBR}
\url{http://internet-browser-review.toptenreviews.com/}.

\bibitem{BS}
\url{http://www.w3schools.com/browsers/browsers_stats.asp}.

\bibitem{TNW08}
F. Schneider, S. Agarwal, T. Alpcan and A. Feldmann, `` The New Web: Characterizing AJAX Traffic,'' In Proc. of the Passive and Active Measurement Conference, 2008.

\bibitem{DM}
``The Data Mining and Knowledge Discovery Handbook,''
In Oded Maimon and Lior Rokach Tel-Aviv (eds.), University Israel, pp. 40-41.

\end{thebibliography}